Safety and Liveness of Unmanned Aerial Vehicle Platoons on Air Highways

### 2016-05-13 docs/AIAA 2016 highway platooning/high_form.tex
Part way through proofreading; currently on page 18, section III-C

The interpretation of \eqref{eq:ahpp} is that we consider air highways to be line segments of constant altitude over a region, and UAV platoons travel on these air highways to get from some origin to some destination. Any UAV flying on a highway over some position $\pos$ incurs a cost of $\cmap(\pos)$, so that the total cost of flying from the origin to the destination is given by \eqref{eq:ahpp}. The air highway placement problem minimizes the cumulative cost of flying from some origin $p^o$ to some destination $p^d$ along the sequence of highways $\hws_N=\{\hw_1, \hw_2, \ldots, \hw_N\}$. The regularization term is used to prevent $N$ from being arbitrarily large.

\begin{figure}
	\centering
	\includegraphics[width=0.95\textwidth]{"fig/highway_illustration"}
	\caption{Highway illustration}
	\label{fig:hw_ill}
\end{figure}

>>>>

The interpretation of \eqref{eq:ahpp} is that we consider air highways to be line segments of constant altitude over a region, and UAV platoons travel on these air highways to get from some origin to some destination. Any UAV flying on a highway over some position $\pos$ incurs a cost of $\cmap(\pos)$, so that the total cost of flying from the origin to the destination is given by the summation in \eqref{eq:ahpp}. The air highway placement problem minimizes the cumulative cost of flying from some origin $p^o$ to some destination $p^d$ along the sequence of highways $\hws_N=\{\hw_1, \hw_2, \ldots, \hw_N\}$. The regularization term is used to prevent $N$ from being arbitrarily large.

\begin{figure}
	\centering
	\includegraphics[width=0.95\textwidth]{"fig/highway_illustration"}
	\caption{Illustration of the air highway placement procedure.}
	\label{fig:hw_ill}
\end{figure}

### 2016-05-13 docs/AIAA 2016 highway platooning/high_sim.tex
Part way through proofreading; currently on page 18, section III-C

This assumption assigns costs in descending order to the categories ``regions around airports'', ``cities'', ``other'', and ``water''. Flying a UAV in each category is more costly by a factor of $b\ge1$ compared to the next most important category. The factor $b$ is a tuning parameter that we adjusted to vary the relative importance of the different categories, and we used $b=4$ in the figures below.

Figure \ref{fig:airHighway_results} shows the San Francisco Bay Area (geographic) map, cost map, cost-minimizing paths, and contours of the value function. The region enclosed by the black boundary represents ``region around airports'', which have the highest cost. The dark blue, yellow, and light blue regions represent the ``cities'', the ``water'', and the ``other''' categories, respectively. We assumed that the origin corresponds to the city ``Concord'', and chose a number of other major cities as destinations.

@@

Figure \ref{fig:airHighway_sparse} shows the result of converting the cost-minimizing paths to a small number of waypoints. The left plot shows the waypoints, interpreted as the start and end points of air highways, over a white background for clarity. The right plot shows these air highways over the map of the Bay Area.

@@

\subsection{Real-Time Highway Location Updates}
Since \eqref{eq:eikonal} can be solved in approximately a second, the air highway placement process can be redone in real-time if the cost map changes. This flexibility can be useful in any situation in which unforeseen circumstances cause a change in the cost of a particular region of the airspace. For example, accidents or disaster response vehicles may result in an area temporarily having a high cost. On the other hand, depending on for instance the time of day, it may be most desirable to fly in different regions of the airspace, resulting in those regions temporarily having a low cost.

>>>>

This assumption assigns costs in descending order to the categories ``regions around airports'', ``cities'', ``other'', and ``water''. Flying a UAV in each category is more costly by a factor of $b$ compared to the next most important category. The factor $b>1$ is a tuning parameter that we adjusted to vary the relative importance of the different categories, and we used $b=4$ in the figures below.

Figure \ref{fig:airHighway_results} shows the San Francisco Bay Area (geographic) map, cost map, cost-minimizing paths, and contours of the value function $V$. The region enclosed by the black boundary represents ``region around airports'', which have the highest cost. The dark blue, yellow, and light blue regions represent the ``cities'', the ``water'', and the ``other''' categories, respectively. We assumed that the origin corresponds to the city ``Concord'', and chose a number of other major cities as destinations.

@@

Figure \ref{fig:airHighway_sparse} shows the result of converting the cost-minimizing paths to a small number of waypoints. The left plot shows the waypoints, interpreted as the start and end points of air highways, over a white background for clarity. The right plot shows these air highways over the map of the Bay Area. Note that we could have gone further to merge some of the overlapping highways. However, the purpose of this section is to illustrate the natural occurrence of air highways from cost-minimizing paths; post-processing of the cost-minimizing paths is not our focus.

@@

\subsection{Real-Time Highway Location Updates}
\MCnote{New section}Since \eqref{eq:eikonal} can be solved in approximately 1 second, the air highway placement process can be redone in real-time if the cost map changes. This flexibility can be useful in any situation in which unforeseen circumstances could cause a change in the cost of a particular region of the airspace. For example, accidents or disaster response vehicles may result in an area temporarily having a high cost. On the other hand, depending on for instance the time of day, it may be most desirable to fly in different regions of the airspace, resulting in those regions temporarily having a low cost.

### 2016-05-13 docs/AIAA 2016 highway platooning/high_waypoints.tex
Part way through proofreading; currently on page 18, section III-C

% !TEX root = main.tex
\subsection{From Paths to Waypoints}
Each of the cost-minimizing paths $\ppath_i$ computed from the solution to the Eikonal equation consists of a closely-spaced set of points. Each path $\ppath_i$ is an approximation to the sequence of highways $\hws_{N_i}^i = \{\hw^i_j\}_{i=1,j=1}^{i=M,j=N_i}$ defined in \eqref{eq:ahpp}, but now indexed by the corresponding path index $i$.

@@

To sparsify the continuous set of points on each path, we start at the destination point and note the path's heading. We add to the collection of waypoints the first point on the path at which the heading changes by some threshold $\theta_C$, and repeat this process along the entire path.

If there is a large change in heading within a small section of the cost-minimizing path, then the collection of points may contain many points which are close together. In addition, there may be multiple paths that are very close to each other (in fact, this behavior is desirable), which may contribute to cluttering the airspace with too many waypoints. We propose to sparsify the waypoints by clustering the points. After clustering, we replace each cluster of points with a single point located at the centroid of the cluster.

To the collection of points resulting from the above process, we add the origin and destination points. Repeating the entire process for every path, we obtain waypoints for all the cost-minimizing paths under consideration. Figure \ref{fig:hw_ill} summarizes the entire air highway placement process.

>>>>

% !TEX root = main.tex
\subsection{From Paths to Waypoints}
\MCnote{Changed wording in this section to say the sparsification of points on a path is not our focus, but just an illustration.}
Each of the cost-minimizing paths $\ppath_i$ computed from the solution to the Eikonal equation consists of a closely-spaced set of points. Each path $\ppath_i$ is an approximation to the sequence of highways $\hws_{N_i}^i = \{\hw^i_j\}_{i=1,j=1}^{i=M,j=N_i}$ defined in \eqref{eq:ahpp}, but now indexed by the corresponding path index $i$.

@@

There are many different ways to sparsify the close-spaced set of points on each path, and this process will not be our focus. However, for illustrative purposes, we show how this process may be started. We begin by noting the path's heading at the destination point. We add to the collection of waypoints the first point on the path at which the heading changes by some threshold $\theta_C$, and repeat this process along the entire path.

If there is a large change in heading within a small section of the cost-minimizing path, then the collection of points may contain many points which are close together. In addition, there may be multiple paths that are very close to each other (in fact, this behavior is desirable), which may contribute to cluttering the airspace with too many waypoints. One way to sparsify the waypoints is to cluster the points. Afterwards, each cluster of points can be replaced by a single point located at the centroid of the cluster.

To the collection of points resulting from the above process, we add the origin and destination points. Repeating the entire process for every path, we obtain waypoints for all the cost-minimizing paths under consideration. Figure \ref{fig:hw_ill} summarizes the entire air highway placement process, including our example of how the closely-space set of points on a path can be sparsified.

### 2016-05-13 docs/AIAA 2016 highway platooning/introduction.tex
Part way through proofreading; currently on page 18, section III-C

% !TEX root = main.tex
\section{Introduction}
Unmanned aerial vehicles (UAVs) have in the past been mainly used for military operations \cite{Tice91}. Recently, however, there has been an immense surge of interest in using UAVs for civil applications. Through projects such as Amazon Prime Air \cite{PrimeAir} and Google Project Wing \cite{ProjectWing}, companies are looking to send UAVs into the airspace to not only deliver commercial packages, but also for important tasks such as aerial surveillance, emergency supply delivery, and search and rescue. In the future, the applications of UAVs are only limited by human imagination.

As a rough estimate, suppose in a city of 2 million people, each person requests a drone delivery every 2 months on average and each delivery requires a 30 minute trip for the drone. This would equate to thousands of vehicles simultaneously in the air just from package delivery services. Applications of UAVs extend beyond package delivery; they can also be used, for example, to provide supplies or to respond to disasters in areas that are difficult to reach but require prompt response \cite{Debusk10,Tornado16}. As a result, government agencies such as the Federal Aviation Administration (FAA) and National Aeronautics and Space Administration (NASA) are also investigating air traffic control for autonomous vehicles in order to prevent collisions among potentially numerous UAVs \cite{FAA13, NASA16}.

Optimal control and game theory are powerful tools for providing liveness and safety guarantees to controlled dynamical systems under bounded disturbances, and various formulations \cite{Bokanowski10,Mitchell05,Barron89} have been successfully used to analyze problems involving small numbers of vehicles \cite{Fisac15,Chen14,Ding08}. These formulations are based on Hamilton-Jacobi (HJ) reachability, which computes the reachable set, defined as the set of states from which a system is guaranteed to have a control strategy to reach a target set of states. Reachability is a powerful tool because reachable sets can be used for synthesizing both controllers that steer the system towards a set of goal states (liveness controllers), and controllers that steer the system away from a set of unsafe states (safety controllers). Furthermore, the HJ formulations are flexible in terms of system dynamics, enabling the analysis of non-linear systems. The power and success of HJ reachability analysis in previous applications cannot be denied, especially since numerical tools are readily available to solve the associated HJ partial differential equation (PDE) \cite{LSToolbox,Osher02,Sethian96}. However, the computation is done on a grid, making the problem complexity scale exponentially with the number of states, and therefore with the number of vehicles. This makes the computation intractable for large numbers of vehicles.

@@

Previous analyses of a large number of vehicles typically do not provide liveness and safety guarantees to the extent that HJ reachability does; however, HJ reachability typically cannot be used to tractably analyze a large number of vehicles. In the second part of this paper, we propose organizing UAVs into platoons, which provide structure that allows pairwise safety guarantees from HJ reachability to better translate to safety guarantees for the whole platoon. With respect to platooning, we first propose a hybrid systems model of UAVs in platoons to establish the modes of operation needed for our platooning concept. Then, we show how reachability-based controllers can be synthesized to enable vehicles to successfully perform mode switching, as well as prevent dangerous configurations such as collisions. Finally, we show several simulations to illustrate the behavior of vehicles in various scenarios.
\MCnote{Slightly weakened claims about guaranteeing safety in last paragraph.}

>>>>

% !TEX root = main.tex
\section{Introduction}
Unmanned aerial vehicles (UAVs) have in the past been mainly used for military operations \cite{Tice91}; however, recently there has been an immense surge of interest in using UAVs for civil applications. Through projects such as Amazon Prime Air \cite{PrimeAir} and Google Project Wing \cite{ProjectWing}, companies are looking to send UAVs into the airspace to not only deliver commercial packages, but also for important tasks such as aerial surveillance, emergency supply delivery, and search and rescue. In the future, the applications of UAVs are only limited by human imagination.

As a rough estimate, suppose in a city of 2 million people, each person requests a drone delivery every 2 months on average and each delivery requires a 30-minute trip for a UAV. This would equate to thousands of UAVs simultaneously in the air just from package delivery services. Applications of UAVs extend beyond package delivery; they can also be used, for example, to provide supplies or to respond to disasters in areas that are difficult to reach but require prompt response \cite{Debusk10,Tornado16}. As a result, government agencies such as the Federal Aviation Administration (FAA) and National Aeronautics and Space Administration (NASA) are also investigating air traffic control for autonomous vehicles in order to prevent collisions among potentially numerous UAVs \cite{FAA13, NASA16}.

Optimal control and game theory are powerful tools for providing liveness and safety guarantees to controlled dynamical systems under bounded disturbances, and various formulations \cite{Bokanowski10,Mitchell05,Barron89} have been successfully used to analyze problems involving small numbers of vehicles \cite{Fisac15,Chen14,Ding08}. These formulations are based on Hamilton-Jacobi (HJ) reachability, which computes the reachable set, defined as the set of states from which a system is guaranteed to have a control strategy to reach a target set of states. Reachability is a powerful tool because reachable sets can be used for synthesizing both controllers that steer the system towards a set of goal states (liveness controllers), and controllers that steer the system away from a set of unsafe states (safety controllers). Furthermore, the HJ formulations are flexible in terms of system dynamics, enabling the analysis of non-linear systems. The power and success of HJ reachability analysis in previous applications cannot be denied, especially since numerical tools are readily available to solve the associated HJ partial differential equation (PDE) \cite{LSToolbox,Osher02,Sethian96}. However, the computation is done on a grid, making the problem complexity scale exponentially with the number of states, and therefore with the number of vehicles. Consequently, HJ reachability computations are intractable for large numbers of vehicles.

@@

Previous analyses of a large number of vehicles typically do not provide liveness and safety guarantees to the extent that HJ reachability does; however, HJ reachability typically cannot be used to tractably analyze a large number of vehicles. In the second part of this paper, we propose organizing UAVs into platoons, which provide a structure that allows pairwise safety guarantees from HJ reachability to better translate to safety guarantees for the whole platoon. With respect to platooning, we first propose a hybrid systems model of UAVs in platoons to establish the modes of operation needed for our platooning concept. Then, we show how reachability-based controllers can be synthesized to enable UAVs to successfully perform mode switching, as well as prevent dangerous configurations such as collisions. Finally, we show several simulations to illustrate the behavior of UAVs in various scenarios.
\MCnote{Slightly weakened claims about guaranteeing safety in last paragraph.}

### 2016-05-13 docs/AIAA 2016 highway platooning/main.tex
Made minor to medium changes according to Claire and Jaime's comments
Updated AIAA 2016 paper; all comments are incorporated
Part way through proofreading; currently on page 18, section III-C

@@

@@

\author{Mo Chen, Qie Hu, Jaime Fisac, Kene Akametalu, Casey Mackin, Claire Tomlin}
\title{Guaranteeing Safety and Liveness of Unmanned Aerial Vehicle Platoons on Air Highways}

@@

\begin{document}

\maketitle

\section*{Nomenclature}
\noindent\begin{tabular}{@{}lcl@{}}
$\cmap$ &=& Cost map \\
$\ccost$ &=& Cumulative cost of a path \\
$\ocost$ &=& Optimal cumulative cost of a path \\
$\hw$ &=& Air highway \\
$\hwd$ &=& Direction of travel of air highway \\
$\hws$ &=& A sequence of air highways \\
$\wpt$ &=& Waypoint \\
$x$ &=& System state (of a vehicle) \\
$\pos=(\pos_x, \pos_y)$ &=& Horizontal position \\
$\vel=(\vel_x, \vel_y)$ &=& Horizontal velocity \\
$\td$ &=& Time limit for descent during potential conflict \\
$\veh{i}$ &=& $i$th vehicle \\
$\vehSCS{i}$ &=& Set of vehicles for vehicle $i$ to consider for safety 
\end{tabular} \\

@@

\section*{Appendix}

>>>>

\usepackage{todonotes} \setlength{\marginparwidth}{2.3cm}

\newcommand{\MCnote}{\todo[size=\footnotesize,author=MC,color=cyan]}

@@

\newcommand{\sepdist}{d_\text{sep}} % separation distance

@@

\author{Mo Chen, Qie Hu, Jaime Fisac, Kene Akametalu, Casey Mackin, Claire Tomlin}
\title{Safety and Liveness of Unmanned Aerial Vehicle Platoons on Air Highways}

@@

\begin{document}
\maketitle
\MCnote{Changed title (used to be ``Guaranteeing Safety ...''}
\section*{Nomenclature}
\noindent\begin{tabular}{@{}lcl@{}}
$\cmap$ &=& Cost map \\
$\ppath$ &=& A path between two points \\
$\ccost$ &=& Cumulative cost of a path \\
$\ocost$ &=& Value function of partial differential equations \\
$\hw$ &=& Air highway \\
$\hwd$ &=& Direction of travel of air highway \\
$\hws$ &=& A sequence of air highways \\
$\wpt$ &=& Waypoint \\
$x$ &=& System state (of a vehicle) \\
$\pos=(\pos_x, \pos_y)$ &=& Horizontal position \\
$\vel=(\vel_x, \vel_y)$ &=& Horizontal velocity \\
$\Pos$ &=& Target position \\
$\Vel$ &=& Target velocity \\
$\sepdist$ &=& Separation distance of vehicles within a platoon \\
$\td$ &=& Time limit for descent during potential conflict \\
$\veh{i}$ &=& $i$th vehicle \\
$\vehSCS{i}$ &=& Set of vehicles for vehicle $\veh{i}$ to consider for safety 
\end{tabular} \\

@@

%\section*{Appendix}

### 2016-05-13 docs/AIAA 2016 highway platooning/plat_controllers.tex
Part way through proofreading; currently on page 18, section III-C

In both of the above cases, we use the dynamics of a single vehicle specified in \eqref{eq:dyn}. The target state would be a position $(\Pos_x, \Pos_y)$ representing the desired merging point on the highway, along with a velocity $(\Vel_x, \Vel_y)$ that corresponds to the speed and direction of travel specified by the highway. For the reachability computation, we define the target set to be a small range of states around the target state $\bar x_H = (\Pos_x, \Pos_y, \Vel_x, \Vel_y)$:

@@

The $i$-th member of the platoon, $Q_{P_i}$, is expected to track a relative position in the platoon $r^i = (r_x^i,r_y^i)$ with respect to the leader's position $p_{P_1}$, and the leader's velocity $v_{P_1}$ at all times. The resulting control law has the form:
\begin{equation}\label{eq:follow}
u^i(t) = k_p \big[p_{P_1}(t) + r^i(t) - p^i(t) \big] + k_v\big[v_{P_1}(t) - v^i(t)\big] + u_{P_1}(t)
\end{equation}
for some $k_p,k_v>0$. In particular, a simple rule for determining $r^i(t)$ in a single-file platoon is given for $Q_{P_i}$ as:
\begin{equation}\label{eq:nominal_pos}
r^i(t) = - (i-1) \sepdist \frac{v_{P_1}}{\|v_{P_1}\|_2}
\end{equation}
where $b$ is the spacing between vehicles along the platoon and $\frac{v_{P_1}}{\|v_{P_1}\|_2}$ is the platoon leader's direction of travel.

>>>>

In both of the above cases, we use the dynamics of a single vehicle specified in \eqref{eq:dyn}. The target state would be a position $(\Pos_x, \Pos_y)$ representing the desired merging point on the highway, along with a velocity $(\Vel_x, \Vel_y)=\vel_\hw$ that corresponds to the speed and direction of travel specified by the highway. For the reachability computation, we define the target set to be a small range of states around the target state $\bar x_H = (\Pos_x, \Pos_y, \Vel_x, \Vel_y)$:

@@

The $i$-th member of the platoon, $Q_{P_i}$, is expected to track a relative position in the platoon $r^i = (r_x^i,r_y^i)$ with respect to the leader's position $p_{P_1}$, and the leader's velocity $v_{P_1}$ at all times. The resulting control law has the form:
\begin{equation}\label{eq:follow}
u^i(t) = k_p \big[p_{P_1}(t) + r^i(t) - p^i(t) \big] + k_v\big[v_{P_1}(t) - v^i(t)\big] + u_{P_1}(t)
\end{equation}
for some $k_p,k_v>0$. In particular, a simple rule for determining $r^i(t)$ in a single-file platoon is given for $Q_{P_i}$ as:
\begin{equation}\label{eq:nominal_pos}
r^i(t) = - (i-1) \sepdist \hwd
\end{equation}
where $\sepdist$ is the spacing between vehicles along the platoon and $\hwd$ is the highway's direction of travel.

### 2016-05-13 docs/AIAA 2016 highway platooning/plat_form.tex
Part way through proofreading; currently on page 18, section III-C

% !TEX root = main.tex
\section{Unmanned Aerial Vehicle Platooning \label{sec:platooning}}
\MCnote{Added introduction to this section}Air highways exhibiting trunk routes that separate near destinations motivate the use of platoons which fly on these highways. The platooning concept provides a structural solution for monitoring and ensuring the safety of a large number of UAVs. The structure imposed by air highways reduces number of pairwise safety checks, and makes pairwise analysis more indicative of the joint safety of all vehicles.

Organizing UAVs into platoons implies that the UAVs cannot fly in an unstructured way, and must have a restricted set of controllers or maneuvers depending on the UAV's role in the airspace. To model UAVs flying in platoons on air highways, we propose a hybrid system whose modes of operations describe the UAV's role in the highway structure. For the hybrid system model, reachability is used to enable successful and safe operation and mode transitions.

@@

\begin{itemize}
\item remain a Leader by traveling along the highway at a pre-specified speed
\item become a Follower by merging the current platoon with a platoon in front
\item become a Free vehicle by leaving the highway
\end{itemize}

@@

\begin{itemize}
\item remain a Follower by staying a distance of $d_\text{sep}$ behind the vehicle in front in the current platoon
\item become a Leader by splitting from the current platoon
\item become a Free vehicle by leaving the highway
\end{itemize}

@@

If a vehicle from any of the other modes malfunctions, it transitions into the Faulty mode. A Faulty vehicle is assumed to descend via a fail-safe mechanism after some pre-specified duration $t_\text{faulty}$ to a different altitude level where it no longer poses a threat to vehicles on the air highway system.
\end{itemize}

@@

We will organize the vehicles into platoons travel along air highways. The vehicles maintain a separation distance of $\sepdist$ with their neighbors inside the platoon. In order to allow for close proximity of the vehicles and the ability to resolve multiple simultaneous safety breaches, we assume that in the event of a malfunction, a vehicle will be able to exit the altitude range of the highway within a duration of $t_\text{faulty}=1.5$. Such a requirement may be implemented practically as an fail-safe mechanism to which the vehicles revert when a malfunction is detected.

>>>>

% !TEX root = main.tex
\section{Unmanned Aerial Vehicle Platooning \label{sec:platooning}}
\MCnote{Added introduction to this section}Air highways exhibiting trunk routes that separate near destinations motivate the use of platoons which fly on these highways. The platooning concept provides a structural solution for monitoring and ensuring the safety of a large number of UAVs. The structure imposed by air highways reduces the number of pairwise safety checks, and makes pairwise analysis more indicative of the joint safety of all UAVs.

Organizing UAVs into platoons implies that the UAVs cannot fly in an unstructured way, and must have a restricted set of controllers or maneuvers depending on the UAV's role in the airspace. To model UAVs flying in platoons on air highways, we propose a hybrid system whose modes of operations describe a UAV's role in the highway structure. For the hybrid system model, reachability analysis is used to enable successful and safe operation and mode transitions.

@@

\begin{itemize}
\item remain a Leader by traveling along the highway at a pre-specified speed $\vel_\hw$
\item become a Follower by merging the current platoon with a platoon in front
\item become a Free vehicle by leaving the highway
\end{itemize}

@@

\begin{itemize}
\item remain a Follower by staying a distance of $d_\text{sep}$ behind the vehicle in front in the current platoon
\item remain a Follower by joining a different platoon on another highway
\item become a Leader by splitting from the current platoon
\item become a Free vehicle by leaving the highway
\end{itemize}

@@

If a vehicle from any of the other modes becomes unable to operate within the allowed set of maneuvers, it transitions into the Faulty mode. Reasons for transitioning to the Faulty mode include vehicle malfunctions, performing collision avoidance with respect to another Faulty vehicle, etc. A Faulty vehicle is assumed to descend via a fail-safe mechanism after some pre-specified duration $t_\text{faulty}$ to a different altitude level where it no longer poses a threat to vehicles on the air highway system. \MCnote{Faulty mode now includes vehicles which could cause additional conflicts by avoiding another faulty vehicle}
\end{itemize}

@@

We will organize the vehicles into platoons travel along air highways. The vehicles maintain a separation distance of $\sepdist$ with their neighbors inside the platoon. In order to allow for close proximity of the vehicles and the ability to resolve multiple simultaneous safety breaches, we assume that when a vehicle exhibits unpredictable behavior, it will be able to exit the altitude range of the highway within a duration of $t_\text{faulty}=1.5$. Such a requirement may be implemented practically as an fail-safe mechanism to which the vehicles revert when needed.
